Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-29 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Set custom scale for distance_1000 map

```{r echo = FALSE, warning=FALSE, message=FALSE}
data(closest_dist)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)
distance_exposure <- county_distance(counties = my_fips,
                                 start_year = 1988, end_year = 2011,
                                 dist_limit = 100)
distance_1000 <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.numeric(value)) %>%
        arrange(desc(value)) %>%
        slice(1:1000)
eastern_states <- c("alabama", "arkansas", "connecticut", "delaware",
                    "district of columbia", "florida", "georgia", "illinois",
                    "indiana", "iowa", "kansas", "kentucky", "louisiana",
                    "maine", "maryland", "massachusetts", "michigan",
                    "mississippi", "missouri", "new hampshire", "new jersey",
                    "new york", "north carolina", "ohio", "oklahoma",
                    "pennsylvania", "rhode island", "south carolina",
                    "tennessee", "texas", "vermont", "virginia",
                    "west virginia", "wisconsin")
map_dist_1000 <- county_choropleth(distance_1000, 
                              title = "Hits by County\nfor Distance < 100 km",
                              legend = "Hits per County", num_colors = 9,
                              state_zoom = eastern_states)
map_dist_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGn", na.value = "white")
```

>>>>

```{r echo = FALSE, warning=FALSE, message=FALSE}
data(closest_dist)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)
distance_exposure <- county_distance(counties = my_fips,
                                 start_year = 1988, end_year = 2011,
                                 dist_limit = 100)
distance_1000 <- distance_exposure %>%
        arrange(desc(storm_dist)) %>%
        group_by(fips) %>%
        summarise(value = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), value = as.numeric(value)) %>%
        arrange(desc(value)) %>%
        slice(1:1000) %>%
        rename(count = value)
distance_1000$value <- cut(distance_1000$count, c(0, 5, 8, 12, 15, 18, 21, 24),
                           labels = c("0-5", "6-8", "9-12", "13-15", "16-18", "19-21", "22-24"),
                           include.lowest = TRUE)
eastern_states <- c("alabama", "arkansas", "connecticut", "delaware",
                    "district of columbia", "florida", "georgia", "illinois",
                    "indiana", "iowa", "kansas", "kentucky", "louisiana",
                    "maine", "maryland", "massachusetts", "michigan",
                    "mississippi", "missouri", "new hampshire", "new jersey",
                    "new york", "north carolina", "ohio", "oklahoma",
                    "pennsylvania", "rhode island", "south carolina",
                    "tennessee", "texas", "vermont", "virginia",
                    "west virginia", "wisconsin")
map_dist_1000 <- county_choropleth(distance_1000, 
                              title = "Hits by County\nfor Distance < 100 km",
                              legend = "Hits per County", num_colors = 7,
                              state_zoom = eastern_states)
map_dist_1000 + scale_fill_brewer("Hits per\nCounty", palette = "YlGn", na.value = "white")
```
